Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/results.tex
Fix conflig

@@

\begin{table}[h]
\centering
\small
\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{ccccc}
\hline
& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
Our&  Useless  & Unclear  & Unclear & Useful \\
Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useful & 3 & 12 & 24 & 94 \\
Useless & 69 & 23 & 7 & 6 \\
Overlap & 1 & 1 & 0 & 1 \\
Undetermined & 12 & 24 & 20 & 21 \\
\hline
\end{tabular}
\label{tb:classify_number}
\end{table}

\textbf{Validation.} After validating our approach using bootstrapping cross validation with 300 iterations, for the random select test datasets, we obtained the results described in Table \ref{}.

%the average of F-measure score are 0.6
%
%After we performed cross validation, we obtained the following result:
%for useful and useless classifications,
%we obtained an average F$_1$ score of 0.693 and 0.681,
%with standard deviation of 0.090 and 0.118, respectively.
%This indicates that we can use our approach to classify with confident of 69.8\%.
%\pick{Precision? Recall?} \thai{This is some confidence interval...}

>>>>

\begin{table}[!t]
\centering
\small
\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{ccccc}
\hline
& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
Our&  Useless  & Unclear  & Unclear & Useful \\
Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useful & 3 & 12 & 24 & 94 \\
Useless & 69 & 23 & 7 & 6 \\
Overlap & 1 & 1 & 0 & 1 \\
Undetermined & 12 & 24 & 20 & 21 \\
\hline
\end{tabular}
\label{tb:classify_number}
\end{table}

@@

\textbf{Validation.} After validating our approach using bootstrapping cross validation with 300 iterations, for the random select test datasets, we obtained the results described in Table \ref{tb:xvalidate}.

%\begin{table*}[!t]
%\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
%\small
%\centering
%\def\arraystretch{1.2}
%\begin{tabular}{ccccccc}
%\hline
%Prediction Models & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
%$\Theta(c,S_T=s_t,D_T=d_t)$   & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \hline
%$\Omega(c,S'_T=s_t,D'_T=d_t)$ & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \hline
%\end{tabular}
%\label{tb:thresholds}
%\end{table*}

\begin{table}[!t]
\caption{Bootstrapping cross validation result of our models}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccc|cc|cc}
\hline
Classifcation & \multicolumn{2}{c|}{F-measure} & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c}{Recall} \\ \cline{2-7}
Models & Avg. & STD. & Avg. & STD. & Avg. & STD. \\ \hline \hline
$\Theta(c,S_T,D_T)$   & 0.693 & 0.089 &  0.654 & 0.116 &  0.759 & 0.123 \\
$\Omega(c,S'_T,D'_T)$ & 0.681 & 0.118 &  0.636 & 0.144 &  0.755 & 0.148 \\
\hline
\end{tabular}
\label{tb:xvalidate}
\end{table}
